Regression Cube Analysis of Cohort Study Data

### 2015-03-30 draft.tex
added Ulis revision

\textbf{Analysis of non-discretized target feature.}
%%
Since our method can analyze numerical target features, as opposed to decision trees used by \emph{UN} before, the analysis was conducted again for the not-dichotomized target using the same formula.
%%
The 3D cube representation already showed lower $R^2$ values in general. However, the analysis is now based on linear regression and the $R^2$ values cannot be directly compared.
%%
The correlation hot spots matched with the ones from the dichotomous target, but were generally lower ($R^2$ of $0.37$ for somatometric features as opposed to $0.58$).
%%
We conclude that the bias introduced by dichotomizing the fat liver content enforces the findings towards liver diseases, while using the numerical features is less expressive.
%%

\textbf{Interleukin-6 correlation with liver fat.}
%%
During the analysis, one hot spot was always observable in the \emph{SI} and \emph{ZF} incorporating a high \emph{Interleukin-6} (\emph{IL-6}) correlation with liver fat values (Fig.~\ref{fig:Application} b).
%%
The correlation was high for both the dichotomized and continuous target feature.
%%
The literature described relations between \emph{IL-6} and liver cancer \cite{He2013} as well as chronic liver diseases \cite{Streetz2003}.
%%
For mice, strong effects of \emph{IL-6} with hepatic steatosis were described \cite{Hong2004}.
%%
The finding is subject of further analysis.
%%
\subsection{Case 2: Hypothesis-free Analysis of the Breast Cancer Data Set}
%%
The analysis aims to find relationships on the breast fat data using features derived from the mammography analysis.
%%
Relationships between the share of parenchyma tissue on the overall breast volume are of high interest \cite{Mccormack2006}.
%%

>>>>

\textbf{Analysis of non-discretized target feature.}
%%
%Since our method can analyze numerical target features, as opposed to decision trees used by \emph{UN} before, the analysis was conducted again for the not-dichotomized target using the same formula.
Since our method can assess numerical target features, the analysis was conducted again for the not-dichotomized target using the same formula.
%%
The 3D cube representation already showed lower $R^2$ values in general. However, the analysis is now based on linear regression and the $R^2$ values cannot be directly compared.
%%
The correlation hot spots matched with the ones from the dichotomous target, but were generally lower ($R^2$ of $0.37$ for somatometric features as opposed to $0.58$).
%%
We assume that the bias introduced by dichotomizing the fat liver content enforces the findings towards liver diseases, while using the numerical features is less expressive.
%%
\textbf{Interleukin-6 correlation with liver fat.}
%%
During the analysis, one hot spot was always observable in the \emph{SI} and \emph{ZF} incorporating a high \emph{Interleukin-6} (\emph{IL-6}) correlation with liver fat values (Fig.~\ref{fig:Application} b).
%%
The correlation was high for both the dichotomized and continuous target feature.
%%
The literature described relations between \emph{IL-6} and liver cancer \cite{He2013} as well as chronic liver diseases \cite{Streetz2003}.
%%
For mice, strong effects of \emph{IL-6} with hepatic steatosis were described \cite{Hong2004}.
%%
The finding is subject of further analysis.
%%
\subsection{Case 2: Hypothesis-free Analysis of the Breast Cancer Data Set}
%%
The analysis aims to find relationships on the breast fat data using features derived from the mammography analysis.
%%
Relationships between the share of parenchyma tissue on the overall breast volume are of high interest \cite{Mccormack2006}.
%%
